\documentclass[letterpaper,12pt]{letter}
\begin{document}
\begin{enumerate}
\item Status Report
\begin{itemize}
\item Date: October 16, 2013
\item Project Title: Fables of Slyvus (C) Monster Minder
\item Team Members: Ryan Nish, Victor Aw, Marissa Melen
\item Completed Work: We have decided on the use of structs for organizing data, as well as using basic text files for data storage outside of the program.  Discussed the use of monster AI, decided to make monsters “egocentric” in spell casting, in that they will cast a healing spell to help themselves and not any ally units.  Human enemies will not have an advanced AI and instead will have a user interface option to allow for the GM to choose whether or not a human enemy has used a spell, and if they have healed an ally unit.  We briefly discussed how to handle the modification of monster stats and any ailments using functions. We are planning on using GTK for the graphical portion of our project.
\item There are currently no tasks that were scheduled and not completed.
\item Scope has changed to include GUI as an expected feature, unless anything goes horribly awry.
\item Next Phase: We will continue to work on implementation and write pseudocode.
\item Anticipated Challenges: While it is unlikely, we may encounter
  challenges in how we can implement the features of our project.
\end{itemize}
\item Our current plan is to work on feature implementation planning for the month of October and then to begin coding.
\item Current project artifacts.
\begin{enumerate}
\item Proposal: We have included the proposal 
\item Analysis documents: We have a nearly analysis document, in LaTeX format
\item Design documents: We have included the feature list 
\item Source code: None right now
\item There are no other essential artifacts
\end{enumerate}
\end{enumerate}
\end{document}
